Data analysis for employee cluster descriptive statistics

### 2023-08-21 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Updated folder path and added some more descriptive

---
title: "Data analysis for employee cluster descriptive statistics"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-08-09.rdata"
  data_file_2: "prep_employees_2023-08-09.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
tictoc::tic()
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("geomtextpath" %in% installed.packages()[,"Package"]))
{
  install.packages("geomtextpath")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
library(tidymodels)
```

@@

@@

@@

@@

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_2, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = sso, y =  prop,fill = .cluster_2)) +
  geom_col(position = "dodge") 
```

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_5, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = sso, y =  prop,fill = .cluster_5)) +
  geom_col(position = "dodge") +
  facet_wrap(facets = vars(sso), scales = "free")
```

@@

@@

@@

@@

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(exit_employment,
       multiple_supervisors,
       gsa_sso) 
```

@@

>>>>

---
title: "Data analysis for employee cluster descriptive statistics"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-08-09.rdata"
  data_file_2: "prep_employees_2023-08-09.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
tictoc::tic()
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("beepr" %in% installed.packages()[,"Package"]))
{
  install.packages("beepr")
}
if(!("geomtextpath" %in% installed.packages()[,"Package"]))
{
  install.packages("geomtextpath")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
library(tidymodels)
```

@@

### Cluster summary statistics

#### Rule-based groups

##### Two clusters

@@

##### Five clusters

@@

#### Exiting employment and multiple supervisors

##### Two clusters

@@

#### SSO

##### Two clusters

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_2, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = .cluster_2, y =  prop,fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(sso), scales = "free_y")
```

##### Five clusters

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_5, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = .cluster_5, y =  prop,fill = .cluster_5)) +
  geom_col(position = "dodge") +
  facet_wrap(facets = vars(sso)
             , scales = "free_y"
             )
```

#### SSO

##### Two clusters

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  count(short_id) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_2, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = .cluster_2, y =  prop,fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(short_id), scales = "free_y")
```

##### Five clusters

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_5, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = .cluster_5, y =  prop,fill = .cluster_5)) +
  geom_col(position = "dodge") +
  facet_wrap(facets = vars(sso)
             , scales = "free_y"
             )
```

@@

High proportion in FAS, GSAIT, OCFO, OGP, OHRM, OSDBU and lower in PBS, OCE, IOA, and OMA.

@@

High proportion in FAS, GSAIT, OCFO, OCR, OGP, OHRM, OSDBU and lower in PBS, OCE, OSC, OSDBU, IOA, and OMA.

@@

High proportion in IOA, OGC, OMA, OSC, and PBS and lower in FAS, GSA IT, OCE, OCFO, OCR, OGP, OHRM, and OSDBU.

@@

High proportion in OAS, and PBS, and lower in FAS, GSA IT, IOA, OCE, OCFO, OCIA, OCR, OGC, OGP, OHRM, OMA, OSC, and OSDBU.

@@

High proportion in FAS, GSA IT, OCE, OCIA, OCR, OSC, and OSDBU and lower in OMA.

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(exit_employment,
       multiple_supervisors) 
```

@@

# CONTINUE FROM HERE

```{r}
beepr::beep(sound = 5)
```

```{r}
